Parameter space representation of Pareto set

### 2013-09-26 concepts.tex
new formal definition of the problem

\section{Preliminaries}

\subsection{Representation}
\begin{defn}
\emph{Configuration}

Let $p_{1},\dots,p_{n}$ be the parameters and $P_{i}$ the domain
of $p_{i}$, i.e. the set of values $v\in P_{i}$ that parameter $p_{i}$
may assume. A configuration is a vector
\[
\mathbf{p}=\left(v_{1},\dots,v_{n}\right)\in P_{1}\times\dots\times P_{n}
\]

\begin{defn}
\emph{Objective function}

Let $o_{1},\dots,o_{m}$ be the objectives and $O_{i}$ the set of
values that $o_{i}$ may assume. Let $O_{i}$ have a ``better than''
operator $\vartriangleright$ defined so that, taking $o_{i},q_{i}\in O_{i}$,
we can always say:
\[
o_{i}\vartriangleright q_{i}\mbox{ (}o_{i}\mbox{ is better than }q_{i}\mbox{)}
\]
 or
\[
o_{i}\vartriangleleft q_{i}\mbox{ (}o_{i}\mbox{ is worse than }q_{i}\mbox{)}
\]
 or
\[
o_{i}\bowtie q_{i}\mbox{ (}o_{i}\mbox{ is neither better nor worse than }q_{i}\mbox{)}
\]

$o_{i}$ can be viewed as a function
\[
o_{i}:\mathbf{p}\rightarrow o_{i}\left(\mathbf{p}\right)\in O_{i},\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
\]
 To take into account all of the objectives, the following function
is defined:
\[
\mathbf{o}:\mathbf{p}\rightarrow\left(o_{1}\left(\mathbf{p}\right),\dots,o_{m}\left(\mathbf{p}\right)\right),\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
\]

%{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
\begin{defn}
\emph{\label{pers02.def:Pareto-set}Pareto set}

Let $U\subseteq P_{1}\times\dots\times P_{n}$. The set of its dominated
configurations is:
\[
Dom\left(U\right)=\left\{ \left.\mathbf{p}\in U\right|\exists\mathbf{x}\in U:o_{i}\left(\mathbf{x}\right)\vartriangleright o_{i}\left(\mathbf{p}\right),\mbox{for }i=1,\dots m\right\} 
\]

Its Pareto set is defined as:
\[
\mathscr{P}\left(U\right)=U\setminus Dom\left(U\right)
\]

When there is no ambiguity, $\mathscr{P}$ is written instead of $\mathscr{P}\left(U\right)$.
\end{defn}

\begin{defn}
\emph{Pareto front}

The Pareto front is the representation in the objective space of the
Pareto set, i.e.:
\[
\mathbf{o}\left(\mathscr{P}\right)\in O_{1}\times\dots\times O_{m}
\]

\end{defn}
On the contrary, we call ``parameter space representation'' of the
Pareto set the representation in which each configuration $\mathbf{p}$
is simply represented as a point of $P_{1}\times\dots\times P_{n}$
space. We will investigate the relation between the ``objective space
representation'' and the ``parameter space representation''. We
are particularly interested in the relation between the evolution
of the objective space representation of the Pareto set and the evolution
of its parameter space representation.

@@

\subsection{Regions}

>>>>

\section{Preliminary Concepts}

\subsection{Formulation of the Problem}

\label{sec:statement_of_the_problem}\index{DSE}

Let $S$ be a parameterized system with $n$ parameters. The generic
parameter $p_i, \ i \in \{1,2,\ldots,n\}$ can take any value in
the set $V_i$. A {\em configuration} $\mathbf{c}$ of the system
$S$ is a $n$-tuple $\langle v_1,v_2,\ldots,v_n \rangle$ in which
$v_i \in V_i$ is the value fixed for the parameter $p_i$. The {\em
configuration space} (or {\em design space}) of $S$ [which we will
indicate as $\mathcal{C}(S)$] is the complete range of possible
configurations [$\mathcal{C}(S) = V_1 \times V_2 \times \ldots
\times V_n$]. Naturally not all the configurations of
$\mathcal{C}(S)$ can really be mapped on $S$. We will call the set
of configurations that can be physically mapped on $S$ the {\em
feasible configuration space} of $S$ [and indicate it as
$\mathcal{C}^*(S)$].

Let $m$ be the number of objectives to be optimized (e.g. power,
cost, performance, etc.). An {\em evaluation function}
$E:\mathcal{C}^*(S)\times \mathcal{B} \longrightarrow \Re^m$ is a
function that associates each feasible configuration of $S$ with
an $m$-tuple of values corresponding to the objectives to be
optimized when any application belonging to the set of benchmarks
$\mathcal{B}$ is executed.

Given a system $S$, an application $b \in \mathcal{B}$ and two
configurations $\mathbf{c}', \mathbf{c}'' \in \mathcal{C}^*(S)$,
$\mathbf{c}'$ is said to {\em dominate} (or {\em eclipse})
$\mathbf{c}''$, and is indicated as $\mathbf{c}' \succ
\mathbf{c}''$, if given $\mathbf{o}'=E(\mathbf{c}', b)$ and
$\mathbf{o}''=E(\mathbf{c}'', b)$ it results that $\mathbf{o}'
\leq \mathbf{o}''$ and $\mathbf{o}' \neq \mathbf{o}''$. Where
vector comparisons are interpreted component-wise and are true
only if all of the individual comparisons are true ($o'_i \leq
o''_i \ \forall \ i = 1,2,\ldots,m$).

The {\em Pareto-optimal set} of $S$ for the application $b$ is the
set:
\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
that is, the set of configurations $\mathbf{c} \in
\mathcal{C}^*(S)$ not dominated by any other configuration.
Pareto-optimal configurations are configurations belonging to the
Pareto-optimal set and the {\em Pareto-optimal front} is the image
of the Pareto-optimal configurations, i.e. the set:
\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} : \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]

The aim of a Design Space Exploration (DSE) strategy is to give a
good approximation of the Pareto-optimal front for a system $S$ and an
application $b$, simulating as few configurations as possible.

%----------------------------------------------------------------

On the contrary, we call ``parameter space representation'' of the
Pareto set the representation in which each configuration $\mathbf{p}$
is simply represented as a point of $P_{1}\times\dots\times P_{n}$
space. We will investigate the relation between the ``objective space
representation'' and the ``parameter space representation''. We
are particularly interested in the relation between the evolution
of the objective space representation of the Pareto set and the evolution
of its parameter space representation.

@@

\subsection{Required Definitions and Concepts}
